Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-21 manuscript/manuscript.tex
Add missing dot

Finally, we computed the gravitational potential $V$ and the vertical component of the
gradient ($g_z$) on a computation grid of $159\times163$ nodes ($0.05^\circ$ spacing on
both longitude and latitude) at a 10km height over the mean Earth radius.
The resulting fields can be seen in Fig.~\ref{fig:neuquen-basin}c-d.
Moreover, we computed the differences between these fields and the ones generated by the
same model but now with a constant density as the mean value between -412kg/m$^3$ and
-275kg/m$^3$, and a linear density that assumes these two values on the highest and the
deepest point of the basin, respectively (Fig.~\ref{fig:neuquen-basin-densities}).
Fig.~\ref{fig:neuquen-basin-diffs}a-b and Fig.~\ref{fig:neuquen-basin-diffs}c-d show the
differences with the constant and the linear density, respectively

>>>>

Finally, we computed the gravitational potential $V$ and the vertical component of the
gradient ($g_z$) on a computation grid of $159\times163$ nodes ($0.05^\circ$ spacing on
both longitude and latitude) at a 10km height over the mean Earth radius.
The resulting fields can be seen in Fig.~\ref{fig:neuquen-basin}c-d.
Moreover, we computed the differences between these fields and the ones generated by the
same model but now with a constant density as the mean value between -412kg/m$^3$ and
-275kg/m$^3$, and a linear density that assumes these two values on the highest and the
deepest point of the basin, respectively (Fig.~\ref{fig:neuquen-basin-densities}).
Fig.~\ref{fig:neuquen-basin-diffs}a-b and Fig.~\ref{fig:neuquen-basin-diffs}c-d show the
differences with the constant and the linear density, respectively.
